Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-25 ms.tex
some clarifications on persistence tests

\begin{figure*}
{\gridline{\fig{persistence_short_log.pdf}{0.49\textwidth}{Short Timescale Persistence}
\fig{persistence_long_lin.pdf}{0.49\textwidth}{Long Timescale Persistence}}}
\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:persistenceAZlab04}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{allan_var_removelinear_False_darkBaseline.pdf}
\caption{The noise in a dark exposure scales with 1/$\sqrt{N}$ for $N$ exposures, as would be expected for white noise.
Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
While 1/f noise substantially increases the noise over the assumption that each \textit{pixel's} read noise is statistically independent, each \textit{integration} is statistically independent.
}\label{fig:darkBaselineAllan}
\end{figure*}

>>>>

\begin{figure*}
{\gridline{\fig{persistence_short_log.pdf}{0.49\textwidth}{Short Timescale Persistence. }
\fig{persistence_long_lin.pdf}{0.49\textwidth}{Long Timescale Persistence}}}
\caption{The NIRCam long wavelength detectors show very rapid charge trap release timescales, such that the count rates fall below the read noise level in 20 seconds.
The data are binned to show that there is no detectable persistence on 3000 second timescales.
An arbitrary offset of 4$e^-$ is added on the short timescale plot to keep the values positive and possible to plot on a log scale.}\label{fig:persistenceAZlab04}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{allan_var_removelinear_False_darkBaseline.pdf}
\caption{The noise in a dark exposure scales with 1/$\sqrt{N}$ for $N$ exposures, as would be expected for white noise.
Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
While 1/f noise substantially increases the noise over the assumption that each \textit{pixel's} read noise is statistically independent, each \textit{integration} is statistically independent when examining this dark (un-illuminated) data.
}\label{fig:darkBaselineAllan}
\end{figure*}
